\documentclass[a4paper,12pt]{article}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{helvet}
%\usepackage[english]{babel}
% Page layout (geometry)
\setlength\voffset{-1in}
\setlength\hoffset{-1in}
\setlength\topmargin{2cm}
\setlength\oddsidemargin{2cm}
\setlength\textheight{25.7cm}
\setlength\textwidth{17.001cm}
\setlength\footskip{0.0cm}
\setlength\headheight{0cm}
\setlength\headsep{0cm}

\setlength\tabcolsep{1mm}
\setlength\parindent{0pt}
\renewcommand\arraystretch{1.3}
\title{}
\author{Mark Zwolinski}
\date{2020-11-15}
\begin{document}

\section*{ELEC2221 D1 Report Form 2023/24}
\textit{This form has a number of boxes to complete. Each box has some example questions that you should answer, but you
may discuss other relevant points. Your answers should be written in complete, grammatically correct, English
sentences. Do not include figures or tables. Other than for the abstract, there is no word limit to each answer, but
the final report must not exceed 2 pages. Use 12pt text. You may delete this instruction text, but do not delete the
section titles or the questions.}


\begin{tabular}{|l|l|l|l|}
\hline
\textbf{Name} &
~
&
\textbf{Email} &
~ \\
\hline
\end{tabular}

\bigskip

\textbf{Abstract }Summarise what you achieved. This is a summary of the report, not an introduction. 100 word limit. \hfill (2 marks)


\bigskip

\textbf{Design and Verification} How did you implement the basic design? What modifications did you make to the code that you were given? How did you use the design software (ModelSim, Quartus and the online checker)? \hfill (3 marks)



\bigskip

\textbf{Extended Design} What additional functionality did you implement? How did you verify and test this extended work? \hfill (3 marks)



\bigskip

\textbf{Reflection }What did you learn from this exercise? What would you do differently if you were to do the exercise
again, and why?\hfill (2 marks)



\bigskip

\end{document}
